---
title: "R Markdown and Leaflet"
author: "Ruchira senanayake"
date: "6/8/2020"
output: html_document
---

# Introduction

In this project we are going to create a web page using R Markdown that features a map created with Leaflet.

we will host our webpage on GitHub Pages.

This page will contain the date that we created the document,a map created with Leaflet.

Let's create the map.
This map will show you some of the [towns in Sri Lanka](https://www.latlong.net/category/towns-210-55.html).

***Loading the data***

```{r, message=FALSE,warning=FALSE,comment=""}
# reading the data
data <- read.csv("towns_srilanka.csv",header = TRUE)

# checking the dimensions of data  
dim(data)
# checking the column names
names(data)
# checking the 1st few rows of data
head(data)
```

***Creating the map using Leaflet***

```{r, message=FALSE,warning=FALSE,comment=""}
# loading the package leaflet
library(leaflet)

# creating the data frame in order to manipulate the data like a table
towns <- data.frame(Town = data$Town,
                    Latitude = data$Latitude,
                    Longitude = data$Longitude)
# creating the map
map <- towns %>%
  leaflet() %>%
  addTiles() %>%
  setView(lat = 7.8731,lng = 80.7718, zoom = 7) %>%
  addMarkers() 
  
# calling the map
map
  
```




























