---
title: "R Markdown Presentation And Plotly"
author: "Ruchira senanayake"
date: "June 8,2020"
output: ioslides_presentation
---

## Introduction

**DATE:June 8,2020**

We are going to reate a web page presentation using R Markdown that features a plot created with Plotly. We will host our webpage on either GitHub Pages. Our webpage will contain the date that we created the document, and a plot created with Plotly.

***Note : We will use the diamond dataset for this task*** 

Lets move on....

## Loading Plotly Package And Diamond Dataset

If you haven't install the **plotly** package install it by using the command `install.packages("plotly")`.

```{r, warning=FALSE, message=FALSE, comment=""}
# loading the plotly package
library(plotly) 

# loading the diamond dataset and assign it to variable data
data <- diamonds[sample(nrow(diamonds), 2500), 
                 c("carat", "price", "clarity", "depth")]
```

## Examine the Diamond Dataset

```{r, warning=FALSE, message=FALSE, comment=""}
# checking the dimensions of the dataset
dim(data) 
# checking the variable names in the dataset
names(data)
```

## Examine the Diamond Dataset

```{r, warning=FALSE, message=FALSE, comment=""}
# examine the descriptive statistics 
summary(data) 
```

## Creating 2D and 3D Scatter Plots

```{r, warning=FALSE, message=FALSE, comment=""}
# 2D plot
plot2D <- plot_ly(data, x = ~carat, y = ~price, color = ~carat,
        size = ~carat, text = ~paste("Clarity: ", clarity))

# 3D plot
plot3D <- plot_ly(data, x = ~carat, y = ~price, z = ~depth,
        color = ~carat, size = ~carat, 
        text = ~paste("Clarity: ", clarity)) 
```

## 2D Plot

```{r, warning=FALSE, message=FALSE, comment=""}
# calling the 2D plot
plot2D
```

## 3D Plot

```{r, warning=FALSE, message=FALSE, comment=""}
# calling the 3D plot
plot3D
```

## THANK YOU!

